### 2021-07-12 README.Rmd
Combined historical and projected dynamics and made the rest of the code base consistent with that. No EWN.

* 2021-06-28 aMSE 0.0.0.2000 The AMSE can now conduct what are effectively retrospective analyses. This is affected by changing the 'CATCHES, 47, if>1 this is the number of historical catch years' line in the control.csv file, which can now be done in a loop using the new 'changevar' function. This has necessitated also changing the 'CEYRS, 20, The first year of catches for which there are CPUE records, ie 1992 is 20th year of catches', which used to take a direct value of how any years of CPUE data there are. We could have just changed two numbers but along that path errors lay.

@@

* zone - highest geogrpahical level. Is simply the totality of the spatial management units.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
rundir <- paste0(ddir,"aMSEUse/scenarios/HS652510")
datadir <- paste0(ddir,"aMSEUse/scenarios/tasdata")
alldirExists(rundir,datadir,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario --------------------- Obviously unhash this to make it work
#out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,
#              hcrfun=mcdahcr,sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#              getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=32,
#              cleanslate=TRUE,verbose=TRUE,doproject=TRUE,ndiagprojs=3)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",glb$pyrs,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "hs652510"
# )

@@

```{r }
#str(out$zoneDP,max.level=1)

>>>>

* 2021_07-12 aMSE 0.0.0.1000 Announcing some rather large changes. Early on in development I made a strategic decision which has proved to make the documentation of the code and implementation of extraction of results overly complex. It is now clear that it was a strategic mistake to separate the historical conditioning from the future projections. Combining them, for purposes of applying a Harvest control rule, or tabulating or plotting results, was adding complexity to every scenario, new plot and table. For example, previously, plots where there were traces of the historical data added to the projections were greatly flawed by having the final year of historical data repeated in the projection data. Obviously, that plotting error could have been solved by selecting which years to plot, instead I decided to simplify everything (for both me and other maintainers) by combining the conditioned dynamic component of the zone and the projection years of the dynamics. Now, in the 'zoneDP' object (see 'out$zoneDP' after a run), for each replicate, we have a continuous set of years from the first year of historical catches out to the last year of the projections. This simplifies everything from the documentation of the code base, the application of the harvest strategy, the plotting of results, basically everything I can think of. The next steps are to expand the results sections and re-write the documentation. The current Tasmania example has now been expanded to 56 populations among the 8 SAU. The fit of the operating model the historical CPUE is now rather improved because now it is possible to include recruitment deviates in the historical conditioning. Currently in the included example it is very ad hoc. One can use ad hoc recruitment deviates or ones derived from some form of localized model fitting. The ad hoc ones currently in use were mainly used to test the new utility functions provided to assist with such things.

@@

* zone - highest geographical level. Is simply the totality of the spatial management units.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/aMSEUse/scenarios/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/aMSEUse/scenarios/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
postdir <- "testnew"  # this is used to label the output HTML file 
rundir <- paste0(ddir,postdir)
datadir <- paste0(ddir,"tasdata")
alldirExists(rundir,datadir,verbose=verbose)
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# HarvestStrategy.R should be in datadir, if it is to be shared by scenarios
source(paste0(datadir,"/TasmanianHS.R"))
# run the scenario --------------------- Obviously unhash this to make it work
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#                  sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#                  getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=50,
#                  cleanslate=TRUE,verbose=TRUE,doproject=doproject,ndiagprojs=4)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# projy <- ifelse(doproject,glb$pyrs,0)
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",projy,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# 
# make_html(replist = replist,  rundir = rundir,  width = 500,  openfile = TRUE,
#           runnotes = runnotes,   verbose = FALSE,  packagename = "aMSE",
#           htmlname = postdir)

@@

```{r }
#str(out$zoneDP,max.level=1)
#str1(out$hcrout)
